Evolution, functional diversity, regime shifts, hysteresis, and nonlinearity; ecosystem responses to environmental change.

### 2021-06-04 manuscript/article.Rmd
Update article.Rmd

```{r}
library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("simulations/r functions/various_useful_functions.r"))
```

@@

>>>>

```{r}
library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("simulations/r functions/various_useful_functions.r"))

##test
```

@@

## Relaxing the biological assumptions of the model
